---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Tracking characteristics of physical advertising across various mediums

This report investigates observations made on the nature and characteristics of 
various different physical advertising mediums, including the impression and effectiveness in engendering actioned on interest. 

First, we load in the data and rename the column names
```{r}
# Load in data
logged_data <-read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTAitmwfV7XPKgW1QcHW65PVqpqmJ_SsYAFvoj34tUaMNqk2mL3PgVSGG8KfQ85QM9164K_Iod9i-vM/pub?output=csv")

# Rename columns
latest_data <- logged_data %>% 
  rename(
    age = 2,
    medium = 3, 
    industry = 4,
    interest = 5,
    act = 6,
    appeal = 7,
    num_sentences = 8,
    num_images = 9,
    gender = 10)

print(latest_data)

```

# Mean reported interest in the physical advertising observed
```{r}
mean_interest = round(mean(latest_data$interest, na.rm = TRUE), 3)

paste0("The mean interest in advertisements out of 5 was ", mean_interest, ".")
```


# Number of sentences in observed physical advertising 
```{r}
mean_num_sentences = round(mean(latest_data$num_sentences, na.rm = TRUE), 3)
max_num_sentences = max(latest_data$num_sentences, na.rm = TRUE)
min_num_sentences = min(latest_data$num_sentences, na.rm = TRUE)

paste0("The minimum number of sentences in an observed physical advertisment was ", min_num_sentences, ". The maximum number of sentences was ", max_num_sentences,". The mean was ",  mean_num_sentences, ".")
```

# Number of images in observed physical advertising 
```{r}
mean_num_images = round(mean(latest_data$num_images, na.rm = TRUE), 3)
max_num_images = max(latest_data$num_images, na.rm = TRUE)
min_num_images = min(latest_data$num_images, na.rm = TRUE)

paste0("The minimum number of images in an observed physical advertisment was ", min_num_images, ". The maximum number of images was ", max_num_images,". The mean was ",  mean_num_images ,  ".")
```

# Bar plot displaying frequency of different advertising mediums
```{r fig.width = 12, fig.height = 8}
latest_data %>%
  ggplot() +
  geom_bar(aes(y = medium)) +
  labs(title = "Frequency of Specific Observed Physical Advertising Mediums",
       x = "Frequency",
       y = "Medium",
       caption = "Source: Physical Advertising Tracking survey")


```

# Bar plot displaying frequency the industry the advertisement is associated with
```{r fig.width = 12, fig.height = 12}
latest_data %>%
  ggplot() +
  geom_bar(aes(y = industry)) +
  labs(title = "Industry Associated with Observed Physical Advertising",
       x = "Frequency",
       y = "Industry",
       caption = "Source: Physical Advertising Tracking survey")


```

# Bar plot displaying frequency of different advertising mediums
```{r fig.width = 12, fig.height = 12}

appeal_formatted <- unlist(strsplit(latest_data$appeal,","))

ggplot() +
  geom_bar(aes(y = appeal_formatted)) +
  labs(title = "Element of Advertisement Found Most Memorable",
       x = "Frequency",
       y = "Element of Advertisement",
       caption = "Source: Physical Advertising Tracking survey")



```