---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background: #FAEBD7 ; 
  color: black;
  font-family: 'Helvetica'
  
}

h1, h3, h4, h2 {
  text-align:center;
  font-weight: 600;
  padding: 30px;
  
}


p {
font-size: 20px;
padding: 0 30px;

}

```

# Tracking Characteristics of Physical Advertising Across Various Mediums

This report investigates observations made on the nature and characteristics of 
various different physical advertising mediums, including the impression and effectiveness in engendering actioned on interest. I wanted to understand common features of physical advertising, who uses it and how it is used, and what elements seem to be most effective.

```{r}
library(tidyverse)
# Load in data
logged_data <-read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTAitmwfV7XPKgW1QcHW65PVqpqmJ_SsYAFvoj34tUaMNqk2mL3PgVSGG8KfQ85QM9164K_Iod9i-vM/pub?output=csv")

# Rename columns
latest_data <- logged_data %>% 
  rename(
    age = 2,
    medium = 3, 
    industry = 4,
    interest = 5,
    act = 6,
    appeal = 7,
    num_sentences = 8,
    num_images = 9,
    gender = 10)
```

## Mean reported interest in the physical advertising observed
```{r}
mean_interest = round(mean(latest_data$interest, na.rm = TRUE), 3)

paste0("The mean interest in advertisements out of 5 was ", mean_interest, ".")
```


## Number of sentences in observed physical advertising 
```{r }
mean_num_sentences = round(mean(latest_data$num_sentences, na.rm = TRUE), 3)
max_num_sentences = max(latest_data$num_sentences, na.rm = TRUE)
min_num_sentences = min(latest_data$num_sentences, na.rm = TRUE)

paste0("The minimum number of sentences in an observed physical advertisment was ", min_num_sentences, ". The maximum number of sentences was ", max_num_sentences,". The mean was ",  mean_num_sentences, ".")
```

## Number of images in observed physical advertising 
```{r }
mean_num_images = round(mean(latest_data$num_images, na.rm = TRUE), 3)
max_num_images = max(latest_data$num_images, na.rm = TRUE)
min_num_images = min(latest_data$num_images, na.rm = TRUE)

paste0("The minimum number of images in an observed physical advertisment was ", min_num_images, ". The maximum number of images was ", max_num_images,". The mean was ",  mean_num_images ,  ".")
```

## What was the most commonly observed medium for physical advertising? 
```{r fig.width = 12, fig.height = 8}
latest_data %>%
  ggplot() +
  geom_bar(aes(y = medium), fill="#654321") +
  labs(title = "Frequency of Specific Observed Physical Advertising Mediums",
       x = "Frequency",
       y = "Medium",
       caption = "Source: Physical Advertising Tracking survey") +
  theme(plot.background = element_rect(fill = "#FAEBD7"),
        panel.background = element_rect(fill = "#D1B399",
                                colour = "#D1B399",
                                size = 0.5, linetype = "solid"),
          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())


```

\n We can see from the above plot that that the most common medium was poster, followed by billboards and bus stops, and then by newspaper and magazines.\n

## What industry was associated with observed physical avertising the most? 
```{r fig.width = 12, fig.height = 12}
latest_data %>%
  ggplot() +
  geom_bar(aes(y = industry), , fill="#654321") +
  labs(title = "Industry Associated with Observed Physical Advertising",
       x = "Frequency",
       y = "Industry",
       caption = "Source: Physical Advertising Tracking survey") +
  theme(plot.background = element_rect(fill = "#FAEBD7"),
        panel.background = element_rect(fill = "#D1B399",
                                colour = "#D1B399",
                                size = 0.5, linetype = "solid"),
          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())


```

\n The above plot suggests that that the most common industry was fashion, followed by beverages, and then by food, hospitality and entertainment, equally.\n

## What elements of the advertsising were most memorable? 
```{r fig.width = 12, fig.height = 12}

appeal_formatted <- unlist(strsplit(latest_data$appeal,","))

ggplot() +
  geom_bar(aes(y = appeal_formatted), , fill="#654321") +
  labs(title = "Element of Advertisement Found Most Memorable",
       x = "Frequency",
       y = "Element of Advertisement",
       caption = "Source: Physical Advertising Tracking survey") +
  theme(plot.background = element_rect(fill = "#FAEBD7"),
        panel.background = element_rect(fill = "#D1B399",
                                colour = "#D1B399",
                                size = 0.5, linetype = "solid"),
          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())



```

\n From the above plot, we can see that that the element of physical advertising that was most memorable was imagery, followed by brand, then product and then copy.
\n